% **************************************************************************************************************
% A Classic Thesis Style
% An Homage to The Elements of Typographic Style
%
% Copyright (C) 2012 Andr\'e Miede http://www.miede.de
%
% If you like the style then I would appreciate a postcard. My address 
% can be found in the file ClassicThesis.pdf. A collection of the 
% postcards I received so far is available online at 
% http://postcards.miede.de
%
% License:
% This program is free software; you can redistribute it and/or modify
% it under the terms of the GNU General Public License as published by
% the Free Software Foundation; either version 2 of the License, or
% (at your option) any later version.
%
% This program is distributed in the hope that it will be useful,
% but WITHOUT ANY WARRANTY; without even the implied warranty of
% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
% GNU General Public License for more details.
%
% You should have received a copy of the GNU General Public License
% along with this program; see the file COPYING.  If not, write to
% the Free Software Foundation, Inc., 59 Temple Place - Suite 330,
% Boston, MA 02111-1307, USA.
%
% **************************************************************************************************************
% Note:
%    * You must not use "u etc. in strings/commands that will be spaced out (use \"u or real umlauts instead)
%    * New enumeration (small caps): \begin{aenumerate} \end{aenumerate}
%    * For margin notes: \marginpar or \graffito{}
%    * Do not use bold fonts in this style, it is designed around them
%    * Use tables as in the examples
%    * See classicthesis-preamble.sty for useful commands
% **************************************************************************************************************
% To Do:
%		 * [high] Check this out: http://www.golatex.de/koma-script-warnung-in-verbindung-mit-listings-package-t2058.html
%    * [medium] mathbb in section-titles/chapter-titles => disappears somehow in headlines!!!
% **************************************************************************************************************
\documentclass[ twoside,openright,titlepage,numbers=noenddot,headinclude,%1headlines,% letterpaper a4paper
                footinclude=true,cleardoublepage=empty,abstractoff, dottedtoc, %listof=numbered,% <--- obsolete, remove (todo)
                BCOR=5mm,paper=a4,fontsize=11pt,%11pt,a4paper,%
                american,%
                ]{scrreprt}

%********************************************************************
% Note: Make all your adjustments in here
%*******************************************************
\input{classicthesis-config}

%%%%%%%%%%%%%%%%%%%%%%%%% START GERBIL Packages %%%%%%%%%%%%%%%%%%%%%%%%%


%********************************************************************
% Hyphenation
%*******************************************************
%\hyphenation{put special hyphenation here}

% ********************************************************************
% GO!GO!GO! MOVE IT!
%*******************************************************
\begin{document}
\frenchspacing
\raggedbottom
%\selectlanguage{american} % american ngerman
%\renewcommand*{\bibname}{all}
%\setbibpreamble{}
\pagenumbering{roman}
\pagestyle{plain}
%********************************************************************
% Frontmatter
%*******************************************************

%\listoftodos


\include{FrontBackmatter/Titlepage}
\cleardoublepage\include{FrontBackmatter/Titleback}
\cleardoublepage\include{FrontBackmatter/Abstract}
\cleardoublepage\include{FrontBackmatter/Publication}
\cleardoublepage\include{FrontBackmatter/Acknowledgments}
\cleardoublepage\input{FrontBackmatter/Acronym.tex} 
\cleardoublepage\include{FrontBackmatter/Contents}
\cleardoublepage\include{FrontBackMatter/Tableofcontent}

\pagestyle{scrheadings}
%********************************************************************
% Mainmatter
%*******************************************************
\pagenumbering{arabic}



\cleardoublepage
\ctparttext{
In the first part, we introduce the core topic of this thesis and motivate its relevance to the research community. 
That is, we want to tackle three research challenges to overcome the separation of the Document Web and the Web of Data to allow users to search both knowledge sources via asking natural language questions. 
Furthermore, we introduce the required preliminaries to comprehend the underlying technologies.
At the end, this part examines the state of the art related to this thesis' topic.
This part covers a wide range of research topics from information extraction and retrieval, to open-science benchmarking and question answering.   
}
\part{Introduction}
\input{part_01/chapter_one.tex}
\input{part_01/chapter_two.tex}
\input{part_01/chapter_three.tex}


\ctparttext{
In the following part, we introduce three novel approaches tackling the \textit{Semantic Gap}.
First, we present a pattern-based algorithm for the annotation of type information from unstructured text.
Second, we describe AGDISTIS -- a knowledge base-agnostic, state-of-the-art system for \acf{NED}. 
Finally, we explain our approach towards Web-scale extraction of \acf{RDF} knowledge from templated websites.  
Those approaches to extract semantic data are designed to form building blocks of even larger information systems.
For example, AGDISTIS is a part of the process pipeline of our hybrid QA system HAWK, introduced in Chapter~\ref{cha:hawk}.
}
\part{Semantic Gap}
\input{part_02/unstructured_annotation/chapter_313.tex} %type annotation
\input{part_02/unstructured_annotation/chapter_311.tex} %Agdistis
\input{part_02/semi_structured_annotation/ISWC_REX/341_rex.tex}


\cleardoublepage
\ctparttext{
The last part explained, how to extract high-quality semantic data from unstructured and semi-structured data sources with scalable algorithms.
However, the multitude of diverse algorithms, especially in the area of semantic annotation of unstructured text, lead to a lack of easily deployable datasets as well as a lack of experiment comparability, repeatability  and archivability.
To close this \textit{Evaluation Gap}, we present an interchangable dataset for \ac{NER} and \ac{NED} as well as an open-science-enabling benchmarking platform for semantic annotation approaches.
Thus, we are able to deliver easily reusable datasets, repeatable experiments and publishable results to our community.
}
\part{Evaluation Gap}
\input{part_02/benchmarking/LREC_N3NIFNERNED/chapter_331.tex}
\input{part_02/benchmarking/WWW_GERBIL/chapter_332.tex}


\cleardoublepage
\ctparttext{
In this part of the thesis, we introduce HAWK, a novel approach for hybrid question answering. 
With this approach, we aim at closing the \textit{Information Gap}.
First, HAWK eliminates the barriers between the structured Web of Data and the Document Web by using both data sources to answer information needs.
Second, HAWK is able to understand natural-language questions which allows users to formulate complex questions without knowing difficult query languages or the underlying data schema.
Thus, our framework leverages the access to unstructured as well as structured knowledge for end-users, laymen and experts as well as non-experts.
}
\part{Information Gap}
\label{part:hybridQA}
\input{part_03/ESWC_HAWK/hawk_full.tex}

\cleardoublepage
\ctparttext{
In the last part of the thesis, we summarize the developed approaches, conclude with the lessons learned and point towards future developments. 
We describe our future research directions which are a natural extension of our previous work.
}
\part{Synopsis}
\input{part_04/summary.tex}

% ********************************************************************
% Backmatter
%*******************************************************

%\cleardoublepage
%\makeatletter
%\@openrightfalse
%\makeatother
\appendix
\part{Appendix}
\renewcommand\thechapter{\Alph{chapter}}
\pagenumbering{Roman}
\cleardoublepage\include{FrontBackmatter/CV}
\cleardoublepage\include{Appendix/AGDISTIS}
\cleardoublepage\include{Appendix/HAWK}
\cleardoublepage\include{FrontBackmatter/Bibliography}
\cleardoublepage\include{FrontBackmatter/Declaration}
% ********************************************************************
% Game Over: Restore, Restart, or Quit?
%*******************************************************
\end{document}
% ********************************************************************
