%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

%\begin{flushright}{\slshape    
%    We have seen that computer programming is an art, \\ 
%    because it applies accumulated knowledge to the world, \\ 
%    because it requires skill and ingenuity, and especially \\
%    because it produces objects of beauty.} \\ \medskip
%    --- \defcitealias{knuth:1974}{Donald E. Knuth}\citetalias{knuth:1974} \citep{knuth:1974}
%\end{flushright}



\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}
I would like to thank all of my colleagues with whom I jointly wrote the papers and articles that led to this work: Axel Ngonga, Sebastian Hellmann, Lorenz B\"uhmann, Tomasso Soru, Jens Lehmann, Mohamed Morsey, Christina Unger, Philipp Cimiano, Konrad H\"offner, Michael R\"oder, Ricardo Usbeck, Anisa Rula, Matteo Palmonari and Denis Lukovnikov.
Special thanks goes to my direct supervisor Dr. Axel-Cyrille Ngonga Ngomo.
He continuously supported me through my Ph. D. work, gave advice and recommendations for further research steps and improvements.
I would like to thank Prof. Dr. Ing. habil. Klaus-Peter F\"ahnrich for his scientific experience with the efficient organization of the process of a Ph. D. thesis and Prof. Dr. S\"oren Auer who helped me to get a scholarship, which made this thesis possible.   
This thesis was funded by the Medienstiftung der Sparkasse Leipzig.
I would like to thank Stephan Seeger for providing me with that opportunity. 
Also, I would like to thank Michael Martin who supervised my master thesis and guided my way to this dissertation. 
I would like to thank my close friend Robert Remus who challenged my ideas constantly and always provided valuable feedback.
Finally I would like to thank my family, Swen, Sylvana, David, Irene and Rolf who have supported me in all respects over the period of this dissertation and beyond. 
\begin{center}
\textit{Thank You.}
\end{center}



\endgroup



